# QR codes for Collection Objects

A QR code can lead to any URL. For sets of Collection Objects with known identifiers - provided from `dinar`, etiquettes and labels with QR codes could be generated in this fashion in various formats

Below we use a public on-line example with a URL embedding an identifier for a bird.

```{r}
library(qrcode)
identifier <- "3c42a44c-096a-445d-b574-22297e96373d"
tgt <- paste0("https://birds.dina-web.net/species/", identifier, ".html")
```

The QR codes below lead to "`r tgt`".

A smaller variant:

```{r, echo=FALSE, cache=FALSE, fig.width=2, fig.height=2, dpi = 150, out.width="300px", out.height="300px"}
qrcode_gen(tgt, ErrorCorrectionLevel = "H", bColor = "Green4")
```

The same thing slightly larger:

```{r, echo=FALSE, cache=FALSE, fig.width=3, fig.height=3, dpi= 150, out.width="600px", out.height="600px"}
qrcode_gen(tgt, ErrorCorrectionLevel = "H", bColor = "Green4")
```

## Automated parameterized reports

Reports written in markdown format can be parameterized and then generated automatically. 

```{r eval=FALSE}
# assumes a markdown report template exists with name "docx-report.Rmd"
# generates output in Word format with a specific value provided for
# the paramterized reports parameter(s)

rmarkdown::render("docx-report.Rmd", output_file = "example-01.docx", 
  params = list(target = "birds.dina-web.net/species/"))

# inspect results using the default app for .docx files
system2("xdg-open", "~/example-01.docx")
```

## Embedding `dinar` calls within ODF documents

Existing Open Document files can be used as report templates by embedding `dinar` calls using a special syntax. 

Here is an example of how a report template in ODT format can be "woven" into a report, embedding `dinar` calls to fetch data from DINA-Web:

```{r eval=FALSE}
library(odfWeave)

# render the report
odfWeave(file = "~/example.odt", dest = "~/example02.odt")

# display it
system2("xdg-open", "~/example01.odt")
```

Although this is possible, it seems to be for the brave and a better approach is probably to use markdown in the report templates.