---
title: "Reports for DINA-Web"
author: "Roger Wilco"
date: "July 26, 2016"
output: bookdown::gitbook
site: bookdown::bookdown_site
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reporting in DINA-Web using markdown

```{r}

```

The `dinar` R-package provides ways and means for working with DINA-Web data - Natural History Collections for the Web - using R to access the DINA-Web REST APIs. 

Combining `dinar` with other R-packages such as `rmarkdown`, `knitr`, `bookdown` provides functionaly to provide reports based on DINA-Web data. 

Output includes both reproducible static canned reports as well as live reports that embed interative content and cover formats such as HTML, PDF and EPUB.

## Compiling books with bookdown

This content is a `bookdown` report that compiles several markdown files together and specifically demonstrate fetching data with `dinar` and authoring a markdown report with QR codes.

## Writing journal articles etc

Instead of `bookdown` the same approach as demonstrated here - ie fetching data with `dinar` and authoring reports - can utilize `rticles` - a package which allows producing articles in formats that adhere to various guidelines required from various journals (JSS, CTeX, R Journal, ACM articles, ACS articles, Elsevier etc)...

## More details

An excellent webinar is available to provide a quick-start tutorial for the `bookdown` package and content authoring using markdown:

- [Webinar about Bookdown](https://www.rstudio.com/resources/webinars/?mkt_tok=eyJpIjoiT0dJMU9EYzBZekUyTldFNCIsInQiOiJtRkJCajB2VlY0a00waGRpbVZDdVkwOVB4TUowcThORlg2SGZLeGZRWHZmNWU3NGNFcU9CUXZjYjNoRUozbmFWWEMrNEVOZ2lLRUpTWlwvcW5yaFBwNUVpT2RcLzI4eUxocnVhbmRvUkxwSDM0PSJ9)


